Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
edits

\newcommand{\LamostGiants}{454180}
\newcommand{\project}[1]{\emph{#1}}
\newcommand{\lamost}{\project{LAMOST}}

@@

The data set of 454180 LAMOST giants was prepared by \citet{ho2017} for use with the supervised machine learning code \textit{The Cannon}. The LAMOST data was shifted to rest frame, normalised, and sampled to a common uniform wavelength grid between 3905 \AA \\ and 9000 \AA. \textit{The Cannon} was used to infer $\text{T}_{\text{eff}}$, log(g), [Fe/H] and [$\alpha$/M] using 9952 common stars between LAMOST and the higher resolution APOGEE survey through the use of a data-driven spectral model, referred to henceforth and simply 'the model'. For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}. The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.

>>>>

\newcommand{\LamostGiants}{454180}
\newcommand{\project}[1]{\emph{#1}}
\newcommand{\lamost}{\project{LAMOST}}
\newcommand{\tc}{\project{The Cannon}}

@@

The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc. The \lamost\ data was shifted to rest frame and continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA. \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model. For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}. The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.
